\documentclass[9pt,letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{bibunits}
\usepackage{fancyhdr}
\usepackage{xcolor}

\renewcommand*{\familydefault}{\sfdefault}

% this line will turn the secondary items from -- into little dots
%\renewcommand{\labelitemii}{$\cdot$}

\renewcommand{\footrulewidth}{0pt}

%to remove "References" headings
\usepackage{etoolbox}
\AtBeginEnvironment{bibunit}{\renewcommand\section[5]{}}

\singlespacing
\pagestyle{fancy}

\pagenumbering{}

\begin{document}
%\rfoot{1/2}

\begin{center}
  {\LARGE \textbf{Barry Van Tassell, PhD}}\\
  \emph{\small (845) 702-2072\\
    bajavata@gmail.com\\
    %{\color{red}https://redmage.tech}\\
    https://github.com/yakbarber}\\
  \line(1,0){450}
\end{center}

\onehalfspacing

{\singlespacing
\noindent \textbf{WORK EXPERIENCE}

{\small
\begin{itemize}
  \item \noindent \textbf{Co-founder, \emph{Liminal Insights Inc (formerly Feasible Inc), Emeryville, CA} \hfill {\scriptsize Apr 2016 to Feb 2023}} 
  {\footnotesize\begin{itemize}

        \item Attended and completed the prestigious Activate (formerly Cyclotron Road) fellowship as a member of their 2016 cohort.
        
        \item Grew the company as a founding member of leadership from having two full-time employees to 37 over 7 years.
        
        \item Remained a major technical contributor and thought leader through the growth of the company from an academic research project to a commercial success with customer contracts for in-line manufacturing equipment.

        
        \item Designed, fabricated, and automated acoustic measurement prototype equipment for battery inspection by integrating custom electronics and software; optimizing measurement performance; and providing support during equipment deployments.
        
        \item Built and maintained the entire codebase for ultrasonic and electrical data acquisition, including backend data conversion and storage, hardware orchestration, microcontroller firmware, and multiple frontends intended for a range of audiences. Since my departure, the codebase continues to be the backbone for existing commercial products.
        
        \item Designed, implemented, and expanded company-wide data ingress pipelines, relational databases, and cloud-based data science tooling in AWS using Terraform to meet internal and external customer requirements.


        \item Authored extensive technical documentation and taught core concepts to the broader company through talks and presentations.

        \item Collaborated across departments to resolve hardware and software issues, develop product requirements, and develop and implement tools to reduce friction in the team's workflow.
        
        \item Configured, hardened, and maintained company office networking and IT infrastructure, including set up and company-wide roll-out of an on-premises VPN.
        
        \item Researched and implemented project management software (Wrike) across the company.

        \item Developed and nurtured a deliberate company culture built around trust, data-driven decisions, well-being, and mutual understanding.

        \item Contributed to the development of an equitable and robust hiring process for technical contributors, led team growth as a hiring manager, and participated in the hiring process for roles across the company.

        %\item built/hired team, multiple roles, attended board meetings, trade shows 

        \item Invented battery analysis and inspection technologies that have resulted in seven granted patents and several additional patents pending.
        
    \end{itemize}}
    
  %\item \noindent Co-founder, \emph{Feasible Inc, Berkeley, CA} \hfill {\scriptsize Apr 2016 to Mar 2022}
  %  {\footnotesize\begin{itemize} 
  %      \item Planned, organized, and led effort to build acoustic and electrochemical data infrastructure
  %      \item Managed multiple projects and team members in fast-pased start-up environment
  %  \end{itemize}}
  \item \noindent \textbf{Postdoctoral Researcher, \emph{Princeton University, Princeton, NJ} \hfill {\scriptsize Oct 2015 to Apr 2016}}
    {\footnotesize\begin{itemize} 
        \item Developed ultrasonic pulser/receivers, transducers, multiplexers, and control software for \\the acoustic analysis of batteries.
    \end{itemize}}
  \item \noindent \textbf{Research Intern, \emph{Microsoft Research, Redmond, WA} \hfill {\scriptsize Jun 2015 to Sep 2015}}
    {\footnotesize\begin{itemize} 
        \item Designed and manufactured flexible batteries with several different chemistries.
        \item Designed multilayer PCBs for Bluetooth Low Energy (BLE) applications, solar energy harvesting, \\battery cycling, and AC-DC and DC-DC power conversion.
    \end{itemize}}
  \item \noindent \textbf{Graduate Researcher, \emph{Princeton University, Princeton, NJ} \hfill {\scriptsize Jun 2013 to May 2015}}
    {\footnotesize\begin{itemize} 
        \item Built and designed an automated, large-scale spray deposition system.
        \item Developed a multi-material reactive spray process to synthesize arbitrary electrode materials on-surface.
        \item Synthesized Li-ion electrode material using an adjustable combination of reactants and conductive filler.
    \end{itemize}}
  \item \noindent \textbf{Graduate Researcher, \emph{The City College of New York, New York, NY} \hfill {\scriptsize Jan 2010 to May 2015}}
    {\footnotesize\begin{itemize} 
        \item Discovered a novel film treatment to prevent dewetting of a polymer dielectric film.
        \item Developed a spray deposition process for nanoparticle dielectric materials for thin film capacitors.
        \item Designed open-sourced hardware and software for inexpensive electrochemical testing.
    \end{itemize}}
  \item \noindent \textbf{Assistant in Instruction (AI), \emph{Princeton University, Princeton, NJ} \hfill {\scriptsize Jul 2013 to Jan 2014}}
    {\footnotesize\begin{itemize} 
        \item Designed lab exercises to teach basic thermodynamics, electronics, and programming.
        \item Performed teaching assistant duties including hands-on teaching of basic electronics and programming.
    \end{itemize}}
  \item \noindent \textbf{Research Intern, \emph{Palo Alto Research Center (PARC), Palo Alto, CA} \hfill {\scriptsize Jan to Jun 2013}}
    {\footnotesize\begin{itemize} 
        \item Designed and authored in-house software for data acquisition, data analysis, and image analysis.
        \item Performed a systematic analysis of gravure printed conductors, dielectrics, and semiconductors.
    \end{itemize}}
\end{itemize}}
}

\begin{center}
  \line(1,0){450}
\end{center}

{\singlespacing
\noindent \textbf{EDUCATION}
\newline
}

{\small
\indent \emph{The City College of New York, New York, NY}

\indent \indent Degree: PhD in Chemical Engineering (2015)

\indent \indent Degree: Master of Engineering in Chemical Engineering (2011)

\indent \emph{University at Buffalo, Buffalo, NY}

\indent \indent Degree: Bachelor of Science in Chemical Engineering (2008)
}

\begin{center}
  \line(1,0){450}
\end{center}

{\singlespacing
\noindent \textbf{CORE SKILLSET}

{\small\begin{itemize}
\item Academic background in chemical engineering, with a research focus on printed electronics and printed batteries
\item Self-taught expertise in full-stack programming, electronics and circuit design, hardware hacking, and the use of software to interface with scientific equipment
\item A curiosity-driven do-it-yourself attitude that leads to unique solutions to difficult problems
\item 8 years of experience with battery inspection and performance analysis using traditional electrical methods and non-destructive acoustic inspection
\item A deep multidisciplinary approach to problem solving
\item Technology proficiencies: Python (incl. NumPy, SciPy, Pandas, scikit-learn, Flask), Rust, TypeScript, JavaScript, Elm, Haskell, Terraform, AWS, Docker, SQL (PostgreSQL, MySQL, SQLite), Linux, Bash, Erlang, RS-232, Wrike, Jira+Confluence, office suites, Arduino/ATMega
\end{itemize}}}


\begin{center}
  \line(1,0){450}
\end{center}

%\newpage

%\rfoot{2/2}

\singlespacing

%\begin{center}
%  {\LARGE \textbf{Barry Van Tassell, PhD}}\\
%  \emph{\small (845) 702-2072\\
%    bajavata@gmail.com}\\
%  \line(1,0){450}
%\end{center}

\onehalfspacing

\noindent \textbf{SELECTED PUBLICATIONS}
\begin{bibunit}[unsrt]
  \small
  \nocite{*}
  \putbib[citations]
\end{bibunit}

%\begin{center}
%  \line(1,0){450}
%\end{center}

%\noindent \textbf{PRESENTATIONS}
%\begin{bibunit}[unsrt]
%  \small
%  \nocite{*}
%  \putbib[citations2]
%\end{bibunit}

\end{document}
